Multidimensional signals and analytic flexibility: Estimating degrees of freedom in human speech analyses

### 2021-05-10 RR_manuscript/Draft_RR.Rmd
:memo: - include sample-size justification and ref to Aczel 2021

In this study, we will follow the data collection procedure proposed by @Parker2020.
The project involves the following five phases:

@@

An online landing page will provide a general description of the project, including a short pre-recorded slide-show that summarizes the data set and research question (<https://many-speech-analyses.github.io>).^["Questions" and "Join Project" buttons will be functioning when recruitment starts. "Join Project" will link to the intake form.]
The project will be advertised via social media, using mailing lists for linguistic and psychological societies, and via word of mouth.^[Terms in small caps in this and later sections are included with their definition in the glossary at the end of the paper for the reader's convenience.]
The target population comprises active speech science researchers with a graduate/doctoral degree (or currently studying for a graduate/doctoral degree) in relevant disciplines.
Researchers can choose to work independently or in a small team.
For the sake of simplicity, we will refer both to a single researcher and teams as \textsc{analysis teams}.
Recruitment for this project will commence upon receiving in-principle acceptance.
As outlined above, our aim is to assess the variability of the reported effects and how these are affected by a set of predictors, rather than the meta-analytic estimate of the investigated effect *per se*.
Given the scarcity of previous meta-analytic studies that directly investigate researcher's degrees of freedom, as reviewed in the introduction, we are not able to establish a properly-grounded minimal sample size.
Thus, we aim to recruit as many teams as possible, within the resource and time limits of the project.

@@

Based on the common practices currently in place within the field, we anticipate that researchers will use multilevel regression models, thus common measurements of effect size, such as Cohen's $d$, may be inappropriate.
Since the variables used by the analysis teams might substantially differ in their measurement scales (e.g, Hertz for frequency vs milliseconds for duration), we will standardize all reported effects by refitting each \textsc{reported model} with centered and scaled continuous variables (*z*-scores, i.e. the observed values subtracted from the mean divided by the standard deviation) and sum-coded factor variables.
Factor-level ordering for each categorical variable will mirror that of the original analyses.
Each \textsc{standardized model} will be fitted as a Bayesian regression model with Stan [@stan2021], RStan [@stan2020a], and brms [@burkner2017] in R [@R-base].
For those reported models that were originally fitted within a frequentist approach, uniform distributions will be used as the priors of all parameters (with the restriction that only positive numbers will be included for scale parameters), to approximate the estimation procedure of frequentist models (i.e. only the distribution of the data determines the posterior distribution).
If a team has fitted Bayesian models, the same priors as reported by the team will be used in fitting the respective standardized model.

@@

## Phase 6: Collaborative Write-Up of Manuscript

>>>>

In this study, we will follow the procedures proposed by @Parker2020 and @aczel2021.
The project involves the following five phases:

@@

An online landing page will provide a general description of the project, including a short pre-recorded slide-show that summarizes the data set and research question (<https://many-speech-analyses.github.io>).^["Questions" and "Join Project" buttons will be functioning when recruitment starts. "Join Project" will link to the intake form.]
The project will be advertised via social media, using mailing lists for linguistic and psychological societies, and via word of mouth.
The target population comprises active speech science researchers with a graduate/doctoral degree (or currently studying for a graduate/doctoral degree) in relevant disciplines.
Researchers can choose to work independently or in a small team.
For the sake of simplicity, we will refer both to a single researcher and teams as \textsc{analysis teams}.^[Terms in small caps in this and later sections are included with their definition in the glossary at the end of the paper for the reader's convenience.]
Recruitment for this project will commence upon receiving in-principle acceptance.
As outlined above, our primary aim is to assess the variability of the reported effects, rather than the meta-analytic estimate of the investigated effect *per se*.
To estimate the degree of uncertainty around effect variability as driven by number of teams, we ran a series of sample size simulations with values of variablity extracted from @silberzahn2018many.
Variability among teams was operationalised as the standard deviation of the teams' reported effects from @silberzahn2018many (which we *z*-scored prior to simulations to make it comparable to our study).
At the mean teams' true standard deviation (0.68 *z*-score), the simulation indicates that the degree of uncertainty around the estimated teams' standard deviation will be below 1 SD at any sample size greater than 10 teams.
We have recieved initial expression of interest to participate from more than 200 analysts, which---even after assuming a 50% drop in participation---we expect to be a sufficient sample size.

@@

Based on the common practices currently in place within the field, we anticipate that researchers will use multilevel regression models, thus common measurements of effect size, such as Cohen's $d$, may be inappropriate.
Furthermore, @aczel2021 suggest that directly asking analysts to report standardized effect sizes could bias the choice of analyses towards types that more straightforwardly return a standardized effect.
Since the variables used by the analysis teams might substantially differ in their measurement scales (e.g, Hertz for frequency vs milliseconds for duration), we will standardize all reported effects by refitting each \textsc{reported model} with centered and scaled continuous variables (*z*-scores, i.e. the observed values subtracted from the mean divided by the standard deviation) and sum-coded factor variables.
Factor-level ordering for each categorical variable will mirror that of the original analyses.
Each \textsc{standardized model} will be fitted as a Bayesian regression model with Stan [@stan2021], RStan [@stan2020a], and brms [@burkner2017] in R [@R-base].
For those reported models that were originally fitted within a frequentist approach, uniform distributions will be used as the priors of all parameters (with the restriction that only positive numbers will be included for scale parameters), to approximate the estimation procedure of frequentist models (i.e. only the distribution of the data determines the posterior distribution).
If a team has fitted Bayesian models, the same priors as reported by the team will be used in fitting the respective standardized model.
Model refitting will also constitute a way of validating the reported analyses, a step recommended by @aczel2021.

@@

## Phase 5: Collaborative Write-Up of Manuscript
